### 2016-03-11 paper/abstract.tex

\begin{abstract}
\yasu{must be at least 70 and at most 150 words.}
\keywords{A; B; C.}
\end{abstract}

>>>>

\begin{abstract}
This paper proposes a novel MAP inference framework for Markov Random
Field (MRF) problems in parallel computing environments.  The inference
framework, dubbed Swarm Fusion method, is a natural generalization of
the Fusion Move method. Every thread (in a case of multi-threading
environments) maintains and updates a solution. At every iteration, a
thread can generate arbitrary number of solution proposals and take
arbitrary number of concurrent solutions from the other threads to
perform multi-way fusion in updating its solution. The framework is
general, making popular existing inference techniques such as
alpha-expansion, fusion move, parallel alpha-expansion, or hierarchical
fusion, its special cases. We have evaluated the effectiveness of our
approach against competing methods on three problems of varying
difficulties, in particular, the stereo, the optical flow, and the
layered depthmap estimation problems.
%Our experiments have shown that the Swarm Fusion method outperform
%competing methods, especially for challenging problems with massive
%solution space.
% can effectively exploits the parallel computing resources and become
%effective especially for challenging problems.
%\yasu{must be at least 70 and at most 150 words.}
\keywords{MRF; Fusion Move; Particle Swarm Optimization}
\end{abstract}

### 2016-03-11 paper/algorithm.tex
yasu

\section{Multi-way particle swarm fusion}
Multi-way Particle Swarm Fusion is a natural extension of Fusion Move
method (FM). We call our method Swarm Fusion (SF) in short. Let us take
a multi-threading environment to explain our idea, while the technique
is also applicable to other parallel programming model such as {\it
MapReduce} in cloud computing.
%

@@

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
thread $T_i$), determining the processing flow of the algorithm: In each
fusion step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool, based on a
user-defined strategy or at random to be simple.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.
Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods. The
 bottom right example shows the general Swarm fusion architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The framework is flexible and
 can realize other data processing architectures depending on the parameters.
 %
 % The left two examples at the
 % bottom row are other Swarm fusion architectures with some restrictions,
 % for which we provide comparative evaluations in
 % Section~\ref{section:results}.
 %
 The left two examples at the bottom are other Swarm fusion
 architectures with some restrictions, to be used for evaluations later.
 %
 It is also easy to verify that existing methods such as
 alpha-expansion~\cite{alpha_expansion}, Fusion move~\cite{FM}, parallel
 alpha-expansion~\cite{delong}, or hierarchical
 fusion~\cite{delong_hierarchical_fusion,olga}, are all special
 cases of the Swarm fusion.}\label{fig:model}
\end{figure}
%
The bottom right architecture is the most general one, in which we
always fuse some solution proposals and some concurrent solutions (i.e.,
$\alpha\ne 0, \beta \ne 0$).
%
Each fusion is multi-way (not binary) with a non-submodular energy, and
we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
inference techniques can be used~\cite{opengm}. For instance, if one
knows that a certain fusion step is a binary fusion with submodular
energy, one can use graph-cuts~\cite{alpha_expansion_paper}. If a
certain fusion step is a binary fusion with non-submodular energy, one
can use QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

>>>>

\section{Multi-way particle swarm fusion}
Multi-way Particle Swarm Fusion is a natural extension of the Fusion
Move method (FM). We call our method Swarm Fusion (SF) in short. Let us
take a multi-threading environment to explain our idea, while the
technique is also applicable to other parallel programming model such as
{\it MapReduce} in cloud computing.
%

@@

Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
thread $T_i$), determining the processing flow of the algorithm: In each
fusion step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool, based on a
user-defined strategy or at random to be simple.
%
% One can further customize how to pick certain proposal generation
% schemes (as in ~\cite{delong}) or solutions.
Swarm Fusion framework is very flexible and yields various data
processing architectures as shown in Figure~\ref{fig:model}.
%
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
 Fusion architecture and its relationships to existing methods. The
 bottom right example shows the general Swarm fusion architecture, where
 each thread takes arbitrary number of solution proposals and concurrent
 solutions from other threads for fusion. The framework is flexible and
 can realize other data processing architectures depending on the parameters.
 %
 % The left two examples at the
 % bottom row are other Swarm fusion architectures with some restrictions,
 % for which we provide comparative evaluations in
 % Section~\ref{section:results}.
 %
 The left two examples at the bottom are other Swarm fusion
 architectures with some restrictions, to be used for evaluations later.
 %
 It is also easy to verify that existing methods such as
 alpha-expansion~\cite{alpha_expansion}, Fusion move~\cite{FM}, parallel
 alpha-expansion~\cite{delong}, or hierarchical
 fusion~\cite{delong_hierarchical_fusion,olga}, are all special
 cases of the Swarm fusion.}\label{fig:model}
\end{figure}
%
The bottom right architecture is the most general one, in which we
always fuse some solution proposals and some concurrent solutions (i.e.,
$\alpha\ne 0, \beta \ne 0$).
%
Each fusion is multi-way (not binary) with a non-submodular energy, and
we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
inference techniques can be used~\cite{opengm}. For instance, if one
knows that a certain fusion step is a binary fusion with submodular
energy, one can use graph-cuts~\cite{alpha_expansion_paper}. If a
certain fusion step is a binary fusion with non-submodular energy, one
can use QPBO~\cite{second_order_smoothness_stereo}.
%
Note that the threads are all synchronized in the figure for a
illustration purpose. In practice, all the threads run asynchronously
with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
%The asynchronous processing could be difficult for cloud parallel
%computing.
%
%
%
\begin{algorithm}
 \caption{Swarm Fusion method}
 \label{algorithm:sf}
 \begin{algorithmic}
  %\Procedure{Swarm Fusion method} {}
  \Procedure{} {$\alpha, \beta$}
  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
  Solution pool
  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
  \ForEach{thread $T_i$}
  \State Initialize its solution $S_i$
  \EndFor
  \State
  \ForEach{thread $T_i$ in parallel till convergence}
  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
  \State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
  \EndFor
  \EndProcedure
 \end{algorithmic}
\end{algorithm}

### 2016-03-11 paper/related_work.tex

\noindent Lempitsky et al. introduces parallel computation to an
alpha-expansion technique, where multiple threads simultaneously fuses
mutually exclusive sets of labels. Kumar et
al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
al.~\cite{delong}, and Veksler~\cite{olga} proposed an hierarchical
approach, where labels can be simultaneously fused from the bottom to
the top in a tree of labels. 
% 
%Strictly speaking, these parallelize alpha-expansion approaches are not
%in the family of Fusion Move methods, because they never generate
%solution proposals. Our approach parallelize fusion move methods.
Instead of taking a hierarchical approach, Batra et
al.~\cite{Dhruv_pushmeet_making_the_right_move} adaptively computed an
effective sequence of labels to explore. This technique can be combined
with parallel alpha-expansion techniques to further obtain speed-up.

@@

\noindent
The core MAP inference algorithms themselves can be parallelized.
Strandmark et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
%
Message passing algorithms are friendly to GPU implementation and can
exploit the power of parallel computation.
%
However, the core optimization libraries are often very complex and
require significant engineering by experts for modification.
%
While state-of-the-art optimization libraries are often freely available
for non-commercial purposes, most companies have to develop and maintain
in-house implementation of these algorithms. The modification of the
core optimization libraries is a significant engineering investment for
many companies. In contrast, our idea is extremely simple and easily
reproducible.

@@

\noindent FM was first introduced by Lempitsky et al. in solving an
optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
used to solve challenging problems in Computer Vision such as a stereo
problem with second order smoothness priors~\cite{woodford}, a stereo
problem with parameteric surface fitting and segmentation (i.e., Surface
Stereo)~\cite{surface_stereo}, or multicut
partitioning~\cite{fusionmovesforcorrelationclustering}.
%
FM has two main advantages over the other general inference
techniques~\cite{trw,loopy_belief_propagation}. First, FM allows us to
exploit domain-specific knowledge in customizing proposal generation
schemes. Second, FM can handle problems with very large label spaces
(and even real-values variables), because the core optimization just
solves a binary decision problem.
%
In contrast, methods like message passing algorithms need to maintain
messages and beliefs for the entire label space all the time.
%
Although conceptually straightforward, we are not aware of {\it parallel
fusion move} algorithms that fuses solution proposals, as opposed to
labels, in parallel. This paper seeks to fully unleash the power of
parallel computation in FM via more general framework.

@@

\noindent
Genetic algorithms (GA)~\cite{ga} and Particle Swarm
Optimization (PSO)~\cite{pso} maintain multiple solutions and improve
them over time.
%
While GA and PSO have limited theoretical justification, they have been
used to produce great empirical results, for example, hand tracking via
PSO~\cite{pushmeet_hand_tracking}. At high level, our strategy is
similar in spirit. However, GA or PSO rather arbitrarily copies part of
the solution or makes random movements in each step. Our approach
directly optimizes the objective function to improve solutions.

>>>>

\noindent Lempitsky et al. introduces parallel computation to an
alpha-expansion technique, where multiple threads simultaneously fuses
mutually exclusive sets of labels. Kumar et
al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
al.~\cite{delong}, and Veksler~\cite{olga} proposed an hierarchical
approach, where labels can be simultaneously fused from the bottom to
the top in a tree of labels. 
% 
Instead of taking a hierarchical approach, Batra et
al.~\cite{Dhruv_pushmeet_making_the_right_move} adaptively computed an
effective sequence of labels to explore. This technique can be combined
with parallel alpha-expansion techniques to further obtain speed-up.
%
Strictly speaking, these approaches are not in the family of FM, because
they only consider constant label proposals. Our approach is a
generalization of FM.

@@

\noindent
The core MAP inference algorithms themselves can be parallelized.
Strandmark et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
%
Message passing algorithms are friendly to GPU implementation and can
exploit the power of parallel computation.
%
%
While state-of-the-art optimization libraries are often freely available
for non-commercial purposes, most companies have to develop and maintain
in-house implementation of these algorithms.  The core optimization
libraries are often very complex and their modifications require
significant engineering investments for many companies. In contrast, our
idea is extremely simple and easily reproducible by standard engineers.

@@

\noindent FM was first introduced by Lempitsky et al. in solving an
optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
used to solve challenging problems in Computer Vision such as a stereo
problem with second order smoothness priors~\cite{woodford}, a stereo
problem with parameteric surface fitting and segmentation (i.e., Surface
Stereo)~\cite{surface_stereo}, or multicut
partitioning~\cite{fusionmovesforcorrelationclustering}.
%
FM has two main advantages over the other general inference
techniques~\cite{trw,loopy_belief_propagation}. First, FM allows us to
exploit domain-specific knowledge in customizing proposal generation
schemes. Second, FM can handle problems with very large label spaces
(and even real-values variables), because the core optimization just
solves a binary decision problem.
%
In contrast, methods like message passing algorithms need to maintain
messages and beliefs for the entire label space all the time.
%
Although conceptually straightforward, we are not aware of {\it Parallel
Fusion Move} algorithms that fuses solution proposals, as opposed to
labels, in parallel. This paper seeks to fully unleash the power of
parallel computation in FM via a more general framework.

@@

\noindent
Genetic algorithms (GA)~\cite{ga} and Particle Swarm
Optimization (PSO)~\cite{pso} maintain multiple solutions and improve
them over time.
%
While GA and PSO have limited theoretical justification, they have been
used to produce great empirical results, for example, hand
tracking~\cite{pushmeet_hand_tracking}. At high level, our strategy is
similar in spirit. However, GA or PSO rather arbitrarily copies part of
the solution or makes random movements in each step. Our approach
directly optimizes the objective function to improve solutions.
